---
title: "Homework 2"
author: "PSTAT 131/231"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
    code_folding: show
---

## Liangchen Xia

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,
                      warning = FALSE)
```

## Linear Regression

For this lab, we will be working with a data set from the UCI (University of California, Irvine) Machine Learning repository ([see website here](http://archive.ics.uci.edu/ml/datasets/Abalone)). The full data set consists of $4,177$ observations of abalone in Tasmania. (Fun fact: [Tasmania](https://en.wikipedia.org/wiki/Tasmania "Tasmania") supplies about $25\%$ of the yearly world abalone harvest.)


The age of an abalone is typically determined by cutting the shell open and counting the number of rings with a microscope. The purpose of this data set is to determine whether abalone age (**number of rings + 1.5**) can be accurately predicted using other, easier-to-obtain information about the abalone.

The full abalone data set is located in the `\data` subdirectory. Read it into *R* using `read_csv()`. Take a moment to read through the codebook (`abalone_codebook.txt`) and familiarize yourself with the variable definitions.

Make sure you load the `tidyverse` and `tidymodels`!

```{r}
library(tidyverse)
library(tidymodels)

```

### Question 1

Your goal is to predict abalone age, which is calculated as the number of rings plus 1.5. Notice there currently is no `age` variable in the data set. Add `age` to the data set.

Assess and describe the distribution of `age`.

```{r}
abalone <- read.csv("abalone.csv")

age<-abalone$rings+1.5

abalone<-abalone %>% mutate(age)

abalone %>% ggplot(aes(x = age)) +
  geom_histogram(bins = 30)

```
The histgram of `age` is positively skewed and the data forms a bell curve skewed to the right. The distribution is centered around 10, and most of abalone have an age around 10 or 12, with a few having an age above 20. 


### Question 2

Split the abalone data into a training set and a testing set. Use stratified sampling. You should decide on appropriate percentages for splitting the data.

```{r}

set.seed(12345)
abalone_split <- initial_split(abalone, prop = 0.8, strata = age)

abalone_train <- training(abalone_split)

abalone_test <- testing(abalone_split)

```

*Remember that you'll need to set a seed at the beginning of the document to reproduce your results.*

### Question 3

Using the **training** data, create a recipe predicting the outcome variable, `age`, with all other predictor variables. Note that you should not include `rings` to predict `age`. Explain why you shouldn't use `rings` to predict `age`.

Steps for your recipe:

1.  dummy code any categorical predictors

2.  create interactions between

    -   `type` and `shucked_weight`,
    -   `longest_shell` and `diameter`,
    -   `shucked_weight` and `shell_weight`

3.  center all predictors, and

4.  scale all predictors.

You'll need to investigate the `tidymodels` documentation to find the appropriate step functions to use.

```{r}

abalone_train<-abalone_train[,-9]

abalone_recipe_1 <- recipe(age ~ ., data = abalone_train) %>% 
  step_dummy(all_nominal_predictors())

abalone_recipe<-abalone_recipe_1 %>%
  step_interact(terms = ~ shucked_weight:starts_with("type")) %>%
  step_interact(terms = ~ longest_shell:diameter) %>%
  step_interact(terms = ~ shucked_weight:shell_weight)  %>% 
  step_center(all_numeric(), -all_outcomes(), -has_role('id variable')) %>% 
  step_scale(all_numeric(), -all_outcomes(), -has_role('id variable')) 

abalone_train_1<-abalone_recipe %>% 
  prep() %>% 
  bake(new_data = abalone_train)

```
We shouldn't use rings to predict age. Because it's in the formula for the age variable. We need find the appropriate step functions by investigate the tidymodels documentation.

### Question 4

Create and store a linear regression object using the `"lm"` engine.

```{r}

lm_model <- linear_reg() %>% set_engine("lm")

```
### Question 5

Now:

1.  set up an empty workflow,
2.  add the model you created in Question 4, and
3.  add the recipe that you created in Question 3.

```{r}
lm_wflow <- workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(abalone_recipe)

lm_wflow
```


### Question 6

Use your `fit()` object to predict the age of a hypothetical female abalone with longest_shell = 0.50, diameter = 0.10, height = 0.30, whole_weight = 4, shucked_weight = 1, viscera_weight = 2, shell_weight = 1.

```{r}
data<-data.frame(type="F",longest_shell=0.5,diameter = 0.10, height = 0.30, whole_weight = 4,
                 shucked_weight = 1, viscera_weight = 2, shell_weight = 1)

data<-tibble(data)

lm_fit <- fit(lm_wflow, abalone_train)

predict(lm_fit, new_data = data)
```

### Question 7

Now you want to assess your model's performance. To do this, use the `yardstick` package:

1.  Create a metric set that includes *R^2^*, RMSE (root mean squared error), and MAE (mean absolute error).
2.  Use `predict()` and `bind_cols()` to create a tibble of your model's predicted values from the **training data** along with the actual observed ages (these are needed to assess your model's performance).
3.  Finally, apply your metric set to the tibble, report the results, and interpret the *R^2^* value.


```{r}
library(yardstick)

#1
abalone_metrics <- metric_set(rmse, rsq, mae)

#2
abalone_train_res <- predict(lm_fit, new_data = abalone_train %>% select(-age))
abalone_train_res <- bind_cols(abalone_train_res, abalone_train %>% select(age))

#3
abalone_metrics(abalone_train_res, truth = age, estimate = .pred)


```
The rsq value is 0.549. Which mean in `age` with `type` + `longest_shell` + `diameter` + `height` + `whole_weight` + `shucked_weight` + `viscera_weight` + `shell_weight`. 54.9% of `age` can be determined by explain these variables.